Efficient Coalition Formation \\ for Web Services

### 2013-07-03 papers/coalition-journal-extension/coalition_journal.tex
Changes

Figure \ref{performanceall} depicts the results of optimal
\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
in \emph{one grand community with many web services} scenario. For
\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally 
intractable and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing well.

@@

>>>>

Figure \ref{performanceall} depicts the results of optimal
\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
in \emph{one grand community with many web services} scenario.

For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the 
taxtation method to relax the core condition for more communities to form. 
We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally 
intractable as number of web services increase and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing well.

@@

As mentioned in section \ref{s:tax}
